### 2024-04-15 docs/projects/datavis/ggplot/ggplotly.qmd
ggplot - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: ggplotly.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

@@

<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-12" style="width:100%;height:400px;"><script data-for="htmlwidget-12" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-12" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895}},"xaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":false,"barmode":"relative","yaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"x","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":37.2602739726027},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","cur_data":"1f2fea5b54d146","source":"A","shinyEvents":["plotly_hover","plotly_click","plotly_selected","plotly_relayout","plotly_brushed","plotly_brushing","plotly_clickannotation","plotly_doubleclick","plotly_deselect","plotly_afterplot","plotly_sunburstclick"],"attrs":{"1f2fea5b54d146":{"x":{},"y":{},"type":"scatter"}},"data":[{"y":[29,29,31,30,26,26,27,26,25,28,27,25,25,25,25,24,25,23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,27,30,26,29,26,24,24,22,22,24,24,17,22,21,23,23,19,18,17,17,19,19,12,17,15,17,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,17,19,17,19,19,17,17,17,16,16,17,15,17,26,25,26,24,21,22,23,22,20,33,32,32,29,32,34,36,36,29,26,27,30,31,26,26,28,26,29,28,27,24,24,24,22,19,20,17,12,19,18,14,15,18,18,15,17,16,18,17,19,19,17,29,27,31,32,27,26,26,25,25,17,17,20,18,26,26,27,28,25,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,19,17,20,17,29,27,31,31,26,26,28,27,29,31,31,26,26,27,30,33,35,37,35,15,18,20,20,22,17,19,18,20,29,26,29,29,24,44,29,26,29,29,29,29,23,24,44,41,29,26,28,29,29,29,28,29,26,26,26],"hoveron":"points","frame":null,"hoverinfo":"text","marker":{"autocolorscale":false,"color":"rgba(0,0,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,0,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":false,"yaxis":"y","x":[1.8,1.8,2.0,2.0,2.8,2.8,3.1,1.8,1.8,2.0,2.0,2.8,2.8,3.1,3.1,2.8,3.1,4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,2.4,2.4,3.1,3.5,3.6,2.4,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,4.7,4.7,4.7,5.2,5.2,3.9,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.0,4.0,4.0,4.0,4.6,5.0,4.2,4.2,4.6,4.6,4.6,5.4,5.4,3.8,3.8,4.0,4.0,4.6,4.6,4.6,4.6,5.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.5,2.5,3.3,2.0,2.0,2.0,2.0,2.7,2.7,2.7,3.0,3.7,4.0,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.0,4.0,4.6,5.0,2.4,2.4,2.5,2.5,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,5.6,3.1,3.8,3.8,3.8,5.3,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,3.4,3.4,4.0,4.7,2.2,2.2,2.4,2.4,3.0,3.0,3.5,2.2,2.2,2.4,2.4,3.0,3.0,3.3,1.8,1.8,1.8,1.8,1.8,4.7,5.7,2.7,2.7,2.7,3.4,3.4,4.0,4.0,2.0,2.0,2.0,2.0,2.8,1.9,2.0,2.0,2.0,2.0,2.5,2.5,2.8,2.8,1.9,1.9,2.0,2.0,2.5,2.5,1.8,1.8,2.0,2.0,2.8,2.8,3.6],"text":["{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 31}","{:x 2.0, :y 30}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.1, :y 27}","{:x 1.8, :y 26}","{:x 1.8, :y 25}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.8, :y 25}","{:x 2.8, :y 25}","{:x 3.1, :y 25}","{:x 3.1, :y 25}","{:x 2.8, :y 24}","{:x 3.1, :y 25}","{:x 4.2, :y 23}","{:x 5.3, :y 20}","{:x 5.3, :y 15}","{:x 5.3, :y 20}","{:x 5.7, :y 17}","{:x 6.0, :y 17}","{:x 5.7, :y 26}","{:x 5.7, :y 23}","{:x 6.2, :y 26}","{:x 6.2, :y 25}","{:x 7.0, :y 24}","{:x 5.3, :y 19}","{:x 5.3, :y 14}","{:x 5.7, :y 15}","{:x 6.5, :y 17}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 3.1, :y 26}","{:x 3.5, :y 29}","{:x 3.6, :y 26}","{:x 2.4, :y 24}","{:x 3.0, :y 24}","{:x 3.3, :y 22}","{:x 3.3, :y 22}","{:x 3.3, :y 24}","{:x 3.3, :y 24}","{:x 3.3, :y 17}","{:x 3.8, :y 22}","{:x 3.8, :y 21}","{:x 3.8, :y 23}","{:x 4.0, :y 23}","{:x 3.7, :y 19}","{:x 3.7, :y 18}","{:x 3.9, :y 17}","{:x 3.9, :y 17}","{:x 4.7, :y 19}","{:x 4.7, :y 19}","{:x 4.7, :y 12}","{:x 5.2, :y 17}","{:x 5.2, :y 15}","{:x 3.9, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 5.2, :y 16}","{:x 5.7, :y 18}","{:x 5.9, :y 15}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 5.2, :y 15}","{:x 5.2, :y 16}","{:x 5.7, :y 17}","{:x 5.9, :y 15}","{:x 4.6, :y 17}","{:x 5.4, :y 17}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 4.2, :y 17}","{:x 4.2, :y 17}","{:x 4.6, :y 16}","{:x 4.6, :y 16}","{:x 4.6, :y 17}","{:x 5.4, :y 15}","{:x 5.4, :y 17}","{:x 3.8, :y 26}","{:x 3.8, :y 25}","{:x 4.0, :y 26}","{:x 4.0, :y 24}","{:x 4.6, :y 21}","{:x 4.6, :y 22}","{:x 4.6, :y 23}","{:x 4.6, :y 22}","{:x 5.4, :y 20}","{:x 1.6, :y 33}","{:x 1.6, :y 32}","{:x 1.6, :y 32}","{:x 1.6, :y 29}","{:x 1.6, :y 32}","{:x 1.8, :y 34}","{:x 1.8, :y 36}","{:x 1.8, :y 36}","{:x 2.0, :y 29}","{:x 2.4, :y 26}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 2.4, :y 31}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 3.3, :y 28}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 3.0, :y 22}","{:x 3.7, :y 19}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 19}","{:x 5.7, :y 18}","{:x 6.1, :y 14}","{:x 4.0, :y 15}","{:x 4.2, :y 18}","{:x 4.4, :y 18}","{:x 4.6, :y 15}","{:x 5.4, :y 17}","{:x 5.4, :y 16}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 2.4, :y 29}","{:x 2.4, :y 27}","{:x 2.5, :y 31}","{:x 2.5, :y 32}","{:x 3.5, :y 27}","{:x 3.5, :y 26}","{:x 3.0, :y 26}","{:x 3.0, :y 25}","{:x 3.5, :y 25}","{:x 3.3, :y 17}","{:x 3.3, :y 17}","{:x 4.0, :y 20}","{:x 5.6, :y 18}","{:x 3.1, :y 26}","{:x 3.8, :y 26}","{:x 3.8, :y 27}","{:x 3.8, :y 28}","{:x 5.3, :y 25}","{:x 2.5, :y 25}","{:x 2.5, :y 24}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 26}","{:x 2.5, :y 23}","{:x 2.2, :y 26}","{:x 2.2, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 3.4, :y 19}","{:x 3.4, :y 17}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 2.2, :y 29}","{:x 2.2, :y 27}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.5, :y 28}","{:x 2.2, :y 27}","{:x 2.2, :y 29}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.3, :y 27}","{:x 1.8, :y 30}","{:x 1.8, :y 33}","{:x 1.8, :y 35}","{:x 1.8, :y 37}","{:x 1.8, :y 35}","{:x 4.7, :y 15}","{:x 5.7, :y 18}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 2.7, :y 22}","{:x 3.4, :y 17}","{:x 3.4, :y 19}","{:x 4.0, :y 18}","{:x 4.0, :y 20}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.5, :y 29}","{:x 2.5, :y 29}","{:x 2.8, :y 23}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 1.9, :y 41}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.5, :y 28}","{:x 2.5, :y 29}","{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 29}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.6, :y 26}"]}]},"evals":[],"jsHooks":[]}</script></div>

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: ggplotly.html}
fontsize: 0.9em
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

@@

<div class="plotly html-widget html-fill-item-overflow-hidden html-fill-item" id="htmlwidget-13" style="width:100%;height:400px;"><script data-for="htmlwidget-13" type="application/htmlwidget-sizing">{"viewer":{"width":"100%","height":400,"padding":"0","fille":true},"browser":{"width":"100%","height":400,"padding":"0","fille":true}}</script><script data-for="htmlwidget-13" type="application/json">{"x":{"config":{"doubleClick":"reset","modeBarButtonsToAdd":["hoverclosest","hovercompare"],"showSendToCloud":false},"layout":{"plot_bgcolor":"rgba(235,235,235,1)","paper_bgcolor":"rgba(255,255,255,1)","legend":{"bgcolor":"rgba(255,255,255,1)","bordercolor":"transparent","borderwidth":1.88976377952756,"font":{"color":"rgba(0,0,0,1)","family":"","size":11.689497716895}},"xaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[2.0,3.0,4.0,5.0,6.0],"zeroline":false,"title":{"text":"displ","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["2.0","3.0","4.0","5.0","6.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"y","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["2.0","3.0","4.0","5.0","6.0"],"categoryorder":"array","range":[1.06,7.54]},"font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187},"showlegend":false,"barmode":"relative","yaxis":{"linewidth":0,"nticks":null,"linecolor":null,"ticklen":3.65296803652968,"tickcolor":"rgba(51,51,51,1)","tickmode":"array","gridcolor":"rgba(255,255,255,1)","automargin":true,"type":"linear","tickvals":[12.0,17.0,22.0,27.0,32.0,37.0,42.0],"zeroline":false,"title":{"text":"hwy","font":{"color":"rgba(0,0,0,1)","family":"","size":14.6118721461187}},"tickfont":{"color":"rgba(77,77,77,1)","family":"","size":11.689497716895},"autorange":false,"showticklabels":true,"showline":false,"showgrid":true,"ticktext":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"ticks":"outside","gridwidth":0.66417600664176,"anchor":"x","domain":[0,1],"hoverformat":".2f","tickangle":0,"tickwidth":0.66417600664176,"categoryarray":["12.0","17.0","22.0","27.0","32.0","37.0","42.0"],"categoryorder":"array","range":[8.8,47.2]},"hovermode":"closest","margin":{"t":25.7412480974125,"r":7.30593607305936,"b":39.6955859969559,"l":37.2602739726027},"shapes":[{"yref":"paper","fillcolor":null,"xref":"paper","y1":1,"type":"rect","line":{"color":null,"width":0,"linetype":[]},"y0":0,"x1":1,"x0":0}]},"highlight":{"on":"plotly_click","persistent":false,"dynamic":false,"selectize":false,"opacityDim":0.2,"selected":{"opacity":1},"debounce":0},"base_url":"https:\/\/plot.ly","cur_data":"1f2fea5b54d146","source":"A","shinyEvents":["plotly_hover","plotly_click","plotly_selected","plotly_relayout","plotly_brushed","plotly_brushing","plotly_clickannotation","plotly_doubleclick","plotly_deselect","plotly_afterplot","plotly_sunburstclick"],"attrs":{"1f2fea5b54d146":{"x":{},"y":{},"type":"scatter"}},"data":[{"y":[29,29,31,30,26,26,27,26,25,28,27,25,25,25,25,24,25,23,20,15,20,17,17,26,23,26,25,24,19,14,15,17,27,30,26,29,26,24,24,22,22,24,24,17,22,21,23,23,19,18,17,17,19,19,12,17,15,17,17,12,17,16,18,15,16,12,17,17,16,12,15,16,17,15,17,17,18,17,19,17,19,19,17,17,17,16,16,17,15,17,26,25,26,24,21,22,23,22,20,33,32,32,29,32,34,36,36,29,26,27,30,31,26,26,28,26,29,28,27,24,24,24,22,19,20,17,12,19,18,14,15,18,18,15,17,16,18,17,19,19,17,29,27,31,32,27,26,26,25,25,17,17,20,18,26,26,27,28,25,25,24,27,25,26,23,26,26,26,26,25,27,25,27,20,20,19,17,20,17,29,27,31,31,26,26,28,27,29,31,31,26,26,27,30,33,35,37,35,15,18,20,20,22,17,19,18,20,29,26,29,29,24,44,29,26,29,29,29,29,23,24,44,41,29,26,28,29,29,29,28,29,26,26,26],"hoveron":"points","frame":null,"hoverinfo":"text","marker":{"autocolorscale":false,"color":"rgba(0,0,0,1)","opacity":1,"size":5.66929133858268,"symbol":"circle","line":{"width":1.88976377952756,"color":"rgba(0,0,0,1)"}},"mode":"markers","type":"scatter","xaxis":"x","showlegend":false,"yaxis":"y","x":[1.8,1.8,2.0,2.0,2.8,2.8,3.1,1.8,1.8,2.0,2.0,2.8,2.8,3.1,3.1,2.8,3.1,4.2,5.3,5.3,5.3,5.7,6.0,5.7,5.7,6.2,6.2,7.0,5.3,5.3,5.7,6.5,2.4,2.4,3.1,3.5,3.6,2.4,3.0,3.3,3.3,3.3,3.3,3.3,3.8,3.8,3.8,4.0,3.7,3.7,3.9,3.9,4.7,4.7,4.7,5.2,5.2,3.9,4.7,4.7,4.7,5.2,5.7,5.9,4.7,4.7,4.7,4.7,4.7,4.7,5.2,5.2,5.7,5.9,4.6,5.4,5.4,4.0,4.0,4.0,4.0,4.6,5.0,4.2,4.2,4.6,4.6,4.6,5.4,5.4,3.8,3.8,4.0,4.0,4.6,4.6,4.6,4.6,5.4,1.6,1.6,1.6,1.6,1.6,1.8,1.8,1.8,2.0,2.4,2.4,2.4,2.4,2.5,2.5,3.3,2.0,2.0,2.0,2.0,2.7,2.7,2.7,3.0,3.7,4.0,4.7,4.7,4.7,5.7,6.1,4.0,4.2,4.4,4.6,5.4,5.4,5.4,4.0,4.0,4.6,5.0,2.4,2.4,2.5,2.5,3.5,3.5,3.0,3.0,3.5,3.3,3.3,4.0,5.6,3.1,3.8,3.8,3.8,5.3,2.5,2.5,2.5,2.5,2.5,2.5,2.2,2.2,2.5,2.5,2.5,2.5,2.5,2.5,2.7,2.7,3.4,3.4,4.0,4.7,2.2,2.2,2.4,2.4,3.0,3.0,3.5,2.2,2.2,2.4,2.4,3.0,3.0,3.3,1.8,1.8,1.8,1.8,1.8,4.7,5.7,2.7,2.7,2.7,3.4,3.4,4.0,4.0,2.0,2.0,2.0,2.0,2.8,1.9,2.0,2.0,2.0,2.0,2.5,2.5,2.8,2.8,1.9,1.9,2.0,2.0,2.5,2.5,1.8,1.8,2.0,2.0,2.8,2.8,3.6],"text":["{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 31}","{:x 2.0, :y 30}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.1, :y 27}","{:x 1.8, :y 26}","{:x 1.8, :y 25}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.8, :y 25}","{:x 2.8, :y 25}","{:x 3.1, :y 25}","{:x 3.1, :y 25}","{:x 2.8, :y 24}","{:x 3.1, :y 25}","{:x 4.2, :y 23}","{:x 5.3, :y 20}","{:x 5.3, :y 15}","{:x 5.3, :y 20}","{:x 5.7, :y 17}","{:x 6.0, :y 17}","{:x 5.7, :y 26}","{:x 5.7, :y 23}","{:x 6.2, :y 26}","{:x 6.2, :y 25}","{:x 7.0, :y 24}","{:x 5.3, :y 19}","{:x 5.3, :y 14}","{:x 5.7, :y 15}","{:x 6.5, :y 17}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 3.1, :y 26}","{:x 3.5, :y 29}","{:x 3.6, :y 26}","{:x 2.4, :y 24}","{:x 3.0, :y 24}","{:x 3.3, :y 22}","{:x 3.3, :y 22}","{:x 3.3, :y 24}","{:x 3.3, :y 24}","{:x 3.3, :y 17}","{:x 3.8, :y 22}","{:x 3.8, :y 21}","{:x 3.8, :y 23}","{:x 4.0, :y 23}","{:x 3.7, :y 19}","{:x 3.7, :y 18}","{:x 3.9, :y 17}","{:x 3.9, :y 17}","{:x 4.7, :y 19}","{:x 4.7, :y 19}","{:x 4.7, :y 12}","{:x 5.2, :y 17}","{:x 5.2, :y 15}","{:x 3.9, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 5.2, :y 16}","{:x 5.7, :y 18}","{:x 5.9, :y 15}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 4.7, :y 17}","{:x 4.7, :y 17}","{:x 4.7, :y 16}","{:x 4.7, :y 12}","{:x 5.2, :y 15}","{:x 5.2, :y 16}","{:x 5.7, :y 17}","{:x 5.9, :y 15}","{:x 4.6, :y 17}","{:x 5.4, :y 17}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 4.2, :y 17}","{:x 4.2, :y 17}","{:x 4.6, :y 16}","{:x 4.6, :y 16}","{:x 4.6, :y 17}","{:x 5.4, :y 15}","{:x 5.4, :y 17}","{:x 3.8, :y 26}","{:x 3.8, :y 25}","{:x 4.0, :y 26}","{:x 4.0, :y 24}","{:x 4.6, :y 21}","{:x 4.6, :y 22}","{:x 4.6, :y 23}","{:x 4.6, :y 22}","{:x 5.4, :y 20}","{:x 1.6, :y 33}","{:x 1.6, :y 32}","{:x 1.6, :y 32}","{:x 1.6, :y 29}","{:x 1.6, :y 32}","{:x 1.8, :y 34}","{:x 1.8, :y 36}","{:x 1.8, :y 36}","{:x 2.0, :y 29}","{:x 2.4, :y 26}","{:x 2.4, :y 27}","{:x 2.4, :y 30}","{:x 2.4, :y 31}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 3.3, :y 28}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 27}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 2.7, :y 24}","{:x 3.0, :y 22}","{:x 3.7, :y 19}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 4.7, :y 12}","{:x 4.7, :y 19}","{:x 5.7, :y 18}","{:x 6.1, :y 14}","{:x 4.0, :y 15}","{:x 4.2, :y 18}","{:x 4.4, :y 18}","{:x 4.6, :y 15}","{:x 5.4, :y 17}","{:x 5.4, :y 16}","{:x 5.4, :y 18}","{:x 4.0, :y 17}","{:x 4.0, :y 19}","{:x 4.6, :y 19}","{:x 5.0, :y 17}","{:x 2.4, :y 29}","{:x 2.4, :y 27}","{:x 2.5, :y 31}","{:x 2.5, :y 32}","{:x 3.5, :y 27}","{:x 3.5, :y 26}","{:x 3.0, :y 26}","{:x 3.0, :y 25}","{:x 3.5, :y 25}","{:x 3.3, :y 17}","{:x 3.3, :y 17}","{:x 4.0, :y 20}","{:x 5.6, :y 18}","{:x 3.1, :y 26}","{:x 3.8, :y 26}","{:x 3.8, :y 27}","{:x 3.8, :y 28}","{:x 5.3, :y 25}","{:x 2.5, :y 25}","{:x 2.5, :y 24}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 26}","{:x 2.5, :y 23}","{:x 2.2, :y 26}","{:x 2.2, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 26}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.5, :y 25}","{:x 2.5, :y 27}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 3.4, :y 19}","{:x 3.4, :y 17}","{:x 4.0, :y 20}","{:x 4.7, :y 17}","{:x 2.2, :y 29}","{:x 2.2, :y 27}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.5, :y 28}","{:x 2.2, :y 27}","{:x 2.2, :y 29}","{:x 2.4, :y 31}","{:x 2.4, :y 31}","{:x 3.0, :y 26}","{:x 3.0, :y 26}","{:x 3.3, :y 27}","{:x 1.8, :y 30}","{:x 1.8, :y 33}","{:x 1.8, :y 35}","{:x 1.8, :y 37}","{:x 1.8, :y 35}","{:x 4.7, :y 15}","{:x 5.7, :y 18}","{:x 2.7, :y 20}","{:x 2.7, :y 20}","{:x 2.7, :y 22}","{:x 3.4, :y 17}","{:x 3.4, :y 19}","{:x 4.0, :y 18}","{:x 4.0, :y 20}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.0, :y 29}","{:x 2.0, :y 29}","{:x 2.5, :y 29}","{:x 2.5, :y 29}","{:x 2.8, :y 23}","{:x 2.8, :y 24}","{:x 1.9, :y 44}","{:x 1.9, :y 41}","{:x 2.0, :y 29}","{:x 2.0, :y 26}","{:x 2.5, :y 28}","{:x 2.5, :y 29}","{:x 1.8, :y 29}","{:x 1.8, :y 29}","{:x 2.0, :y 28}","{:x 2.0, :y 29}","{:x 2.8, :y 26}","{:x 2.8, :y 26}","{:x 3.6, :y 26}"]}]},"evals":[],"jsHooks":[]}</script></div>

### 2024-04-15 docs/projects/datavis/ggplot/ggplotly_cont.qmd
ggplot - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: ggplotly_cont.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

@@

::: {.sourceClojure}
```clojure
(ns ggplotly-cont
  (:require [tablecloth.api :as tc]
            [scicloj.metamorph.ml.toydata.ggplot :as toydata.ggplot]
            [tech.v3.datatype.functional :as fun]
            [scicloj.kindly.v4.kind :as kind]
            [clojure.string :as str]
            [clojure.math :as math]))
```
:::

@@

@@

::: {.sourceClojure}
```clojure
:ok
```
:::

::: {.printedClojure}
```clojure
:ok

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: ggplotly_cont.html}
fontsize: 0.9em
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

@@

::: {.sourceClojure}
```clojure
(ns ggplotly-cont
  (:require [tablecloth.api :as tc]
            [scicloj.metamorph.ml.toydata.ggplot :as toydata.ggplot]
            [tech.v3.datatype.functional :as fun]
            [scicloj.kindly.v4.kind :as kind]
            [clojure.string :as str]
            [clojure.math :as math]
            [clojure2d.color :as color]))
```
:::

@@

::: {.sourceClojure}
```clojure
(color/palette )
```
:::

::: {.printedClojure}
```clojure
[[223.0 46.0 40.0 255.0]
 [254.0 128.0 26.0 255.0]
 [233.0 191.0 53.0 255.0]
 [129.0 187.0 66.0 255.0]
 [50.0 199.0 169.0 255.0]
 [74.0 155.0 220.0 255.0]]

@@

### 2024-04-15 docs/projects/datavis/ggplot/index.qmd
ggplot - rerendered

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: index.html}
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: cosmo, output-file: index.html}
fontsize: 0.9em
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}
